The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-05 src/ms.tex
Replace "federal" with "US federal"

\begin{description}
    \item[Moore] The Gordon and Betty Moore Foundation awarded the Astropy
    project a $\sim$\$900k (US) grant in 2019 for the proposal ``Sustaining and
    Growing the Astropy Project.'' Over a three-year term, this grant supported
    sustenance of the Project by providing funds for (1) the development and
    maintenance of the \astropypkg and its infrastructure, provided to existing
    project members and targeted hires, (2) the transition of long-term users to
    contributors and maintainers through mentorship efforts, (3) the
    formalization of a governance structure (see
    Section~\ref{sec:project-governance}), and (4) the improvement of equity,
    diversity, and inclusion efforts in the project (see
    Section~\ref{sec:project-ide}). Some of this money supported travel for
    meetings, conferences, and workshops. This generous grant helped reduce
    reliance on volunteer-driven maintenance of the openly-developed package and
    paved the way to acquire funding from federal agencies, representing a major
    milestone for the success of the project.

>>>>

\begin{description}
    \item[Moore] The Gordon and Betty Moore Foundation awarded the Astropy
    project a $\sim$\$900k (US) grant in 2019 for the proposal ``Sustaining and
    Growing the Astropy Project.'' Over a three-year term, this grant supported
    sustenance of the Project by providing funds for (1) the development and
    maintenance of the \astropypkg and its infrastructure, provided to existing
    project members and targeted hires, (2) the transition of long-term users to
    contributors and maintainers through mentorship efforts, (3) the
    formalization of a governance structure (see
    Section~\ref{sec:project-governance}), and (4) the improvement of equity,
    diversity, and inclusion efforts in the project (see
    Section~\ref{sec:project-ide}). Some of this money supported travel for
    meetings, conferences, and workshops. This generous grant helped reduce
    reliance on volunteer-driven maintenance of the openly-developed package and
    paved the way to acquire funding from US federal agencies, representing a
    major milestone for the success of the project.
